---
title: "fn_ARSS {Morefi} "
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_ARSS {Morefi}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Coincident Curves Test

## Description

The function `fn_ARSS` perform the Coincident Curves Test, to determine if there
are significant differences between the fitted curves for each database. It is 
based on the Analysis of the Residual Sum of Squares (ARSS) (Chen et al. 1992).


$$F=\frac{\frac{RSS_{p}-RSS_{s}}{3\bullet \left( K-1 \right)}}{\frac{RSS_{s}}{N-3\bullet K}}$$

$RSS_{p}$= RSS of each regression fitted by pooled data, $RSS_{s}$= sum of the 
RSS of each regression fitted for each individual sample, **N**= total sample 
size, and **K** = number of samples in the comparison.


The residual sum of squares (RSS) and the degrees of freedom (DF) for each 
fitted regression are previously stored in the `List_TCCT` list. For each 
regression, the calculations are stored in a data frame `T1`, which is stored
iteratively using a loop for in a list `T`.


Inside the function, the RSS and DF for the joined sample are calculated to 
perform the F test for two tails $\alpha/2$. The decision criteria is performed:
"*" if $p-value\le \alpha$ or "NS" if the $p-val\gt \alpha$.


The function requires defining:

 * **List_TCCT**: A list with fitted regression results.  
 * **i**:  An integer value indicating the ith regression analyzed.
 * **alfa**: A numerical value that defines the significance level. The default number is 0.05.


Seealso: `FDist` from the package stats (version 3.6.2)


## fn_ARSS

The function is included in the `Morefi` package **Morphological Relationships 
Fitted by Robust Regression**.


```{r setup}
library(Morefi)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
fn_ARSS <- function(List_TCCT, i,  alfa= 0.05){
  T  <- list()
  for (i in 1:length(List_TCCT)){
  
  T1 <- List_TCCT[[i]]
  lvar <- names(List_TCCT[i])

  T1[1,1] <- paste0(substr(lvar,1,2)," vs. ",
                    substr(lvar,3,nchar(lvar)))
  # RSSs sum of the RSS of each regression fitted
  T1[4,3] <- round(sum(as.numeric(T1[1,3]),
                       as.numeric(T1[2,3])),2)

  # DF Sum GL1 + GL2
  T1[4,4] <- sum(as.numeric(T1[1,4]),as.numeric(T1[2,4]))

  # F calculated (Fc)
  T1[1,5] <- round(abs((as.numeric(T1[3,3])-as.numeric(T1[4,3]))/
                         as.numeric(T1[4,3])),4)

  # F table (critical value)
  T1[1,6] <- round(qf(alfa, as.numeric(T1[3,4]),
                      as.numeric(T1[4,4]),
                      lower.tail= FALSE),4)

  # p-value for two tails
  P_value <- pf(as.numeric(T1[1,6]),
                as.numeric(T1[4,4]),
                as.numeric(T1[3,4]),
                lower.tail=FALSE)

  T1[1,7] <- if(P_value>1-alfa){
    "p>0.95"
  } else {
    format(P_value, format= "e", digits = 4)
  } # End if

  # Decision criteria
  T1[1,8] <-  if(P_value>alfa){
    "NS"
  } else {
    "*"
  } # End if
  T[[i]] <- as.data.frame(T1)
  } # End for
  return(T)
}  # End function
```


## Examples

The length-weight was estimated for the Pacific Sierra *Scomberomorus sierra*
by sex and the total sample (Unpublish data). The sex of 362 organisms was 
determined: 95 were females and 118 males. The adjusted models show the following
data: Females SSR= 1557970.877 and DF= 93; Males SSR= 1188689.721 and DF= 116; and 
the total sample SSR= 2045176.876 and DF= 211. Values are stored in the table 
`Table_CC`, this is stored in a list, and the name of each item is built with 
the acronyms of the model variables (e.g. LTWT).

```{r, warning=FALSE, message=FALSE, results='asis'}
Table_CC <- data.frame(matrix(NA,nrow=4,ncol=8))
Table_CC[1,1] <- "Lt-WT" 
Table_CC[,2] <- c("Females","Males","Total","Joined")
colnames(Table_CC) <- c("Model","Category","RSS","DF","ARSS","F-table","p-value","Criteria")

Table_CC[1,3] <- 1557970.877
Table_CC[1,4] <-  93 
Table_CC[2,3] <- 1188689.721
Table_CC[2,4] <-  116 
Table_CC[3,3] <- 2045176.876
Table_CC[3,4] <-  211 


List_ARSS <- list(LTWT=Table_CC)

i <- 1

ARSS <- fn_ARSS(List_ARSS, i,  alfa= 0.05)
ARSS
```


## References

Chen Y., Jackson, D. A., & Harvey, H. H. 1992. A comparison of von Bertalanffy and polynomial functions in modelling fish growth data. Can. J. Fish. Aquat. Sci. 49(6): 1228–1235. https://doi.org/10.1139/f92-13
