---
title: "fn_fyield {Morefi} "
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_fyield {Morefi}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Fillet yield 


## Description


The function calculates the fillet yield by dividing a defined weight reference 
point `bm` by the mean, lower, and upper confidence interval of 95% (IC95%) of 
the estimated fillet weight, respectively. These values are obtained from the 
list items `l_intervals$CI` returned by the function `Morefi::fn_intervals()`.


If the analyzed regression has fillet weight as an independent variable,
then values are calculated. An "if statement" is written for this propose.


Fillet yield was calculated for a sequence of the independent variable
(including minimum and maximum values).


Inside the function, the mean (Ymean), lower (Ymin), and upper (Ymax) CI95%
are stored in a table (Table_Y).


The function requires defining:

 * **i**: An integer value that indicates which regression analysis to use.
 * **bm**: An integer value used as a benchmark.
 * **df**: A data frame with landed weights for each category.
 
 
Seealso: fn_intervals(): customized for the present package
         mutate(): from the package dplyr (version 1.0.10)


## fn_fyield

The function is included in the `Morefi` package **Morphological Relationships Fitted by Robust Regression**.


```{r setup}
library(Morefi)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
fn_fyield <- function(i,bm,df){
                  Table_Y <- df
                  Table_Y <- dplyr::mutate(Table_Y,
                                           Yfit=   bm/Table_Y[,2],
                                           YIC_L=  bm/Table_Y[,3],
                                           YIC_U=  bm/Table_Y[,4],
                                           YIP_L=  bm/Table_Y[,5],
                                           YIP_U=  bm/Table_Y[,6]
                                           )
                  return(Table_Y)
            }   # End fn
```


## Examples

Do not execute, it's just a syntax example.
<!-- Falta describir el ejemplo y que corra.... -->

```{r, warning=FALSE, message=FALSE, eval = FALSE}
FY <- fn_fyield(i,bm,df)
