---
title: "fn_freqw {Morefi}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_freqw {Morefi}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Percentage frequencies of weights

## Description

The function `fn_freqw` is a methodological function to calculate the percentage frequencies of weights by model adjusted using the robust regression approach.

The function calculates the relative frequency distribution using the function `fn_freq` from `Morefi` package.

For `fn_freq`, the breaks object must be defined. For this work, a sequence of breakpoints of equal distance is used. To incorporate the number of non-weighted values $(w_{i}=1)$, a class interval **1** is added to the sequence.


A table with frequencies by class interval is returned.


The function requires defining:

 * **df**: A vector of data values.  
 * **breaks**: A vector with class intervals.
 * **right**: Logical, indicating if the intervals should be closed on the right (and open on the left) or vice versa.


Seealso: `cut()` and `table()` functions from the R base package.
       : `fn_freq` from `Morefi` package


## fn_freqw

The function is included in the `Morefi` package **Morphological Relationships 
Fitted by Robust Regression**.


```{r setup}
library(Morefi)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
fn_freqw <- function(df, breaks, right=FALSE){
                    freq <- fn_freq(df, breaks, right=FALSE)
                    nw <- length(which(df ==1))
                    freq <- c(freq, nw)
                    freq <-  100*freq/length(df)
                    }
```


## Examples

 In the "df" object, 30 random values between 0.1 and 0.9 are generated and five values equal to 1 are added.
 The breaks object is a sequence of equal distances, to incorporate the number of non-weighted values (wi=1), a class interval "1" is added to the sequence.


```{r, warning=FALSE, message=FALSE, results='asis'}
df <- c(runif(n=30, min=0, max=1),rep(1,5))
breaks  <-  c(seq(0.1,0.9, by=0.1),1)

freq <- fn_freqw(df, breaks, right=FALSE)
freq
```

## References

Yau C (2024, deck 25). Frequency Distribution of Quantitative
Data. R Tutorial An R Introduction to Statistics.
https://www.r-tutor.com/elementary-statistics/quantitative-data/frequency-distribution-quantitative-data
