---
title: "fn_intervals {Morefi} "
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_intervals {Morefi}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Non parametric confidence intervals

## Description


The function calculates a non parametric confidence and predicted intervals
using the function predFit from the package investr (version 1.4.2)


The function requires defining:


 * **xseq**: A vector with a sequence for independent variable.
 * **eq**: Summary of the equation fitted.
 

The function return a data frame `df` with the xseq (x1), the fitted values for 
dependent variable (fit), the low and upper confident (IC_L and IC_U) and 
predicted intervals (IP_L and IP_U).


seealso: predFit() from the package investr (version 1.4.2)


## fn_intervals

The function is included in the `Morefi` package Morphological Relationships Fitted by Robust Regression.


```{r setup}
library(Morefi)
```


The function is detailed below.


```{r, warning=FALSE, message=FALSE}

fn_intervals <- function(eq,xseq){
                    new.data <- as.data.frame(xseq)
                    str(predFit(eq, new.data, se.fit = TRUE))
                    CI95 <- predFit(eq, newdata = new.data,
                                    interval = "confidence",level=0.95)
                    PI95 <- predFit(eq, newdata = new.data,
                                    interval = "prediction",level=0.95)

                    df <- as.data.frame(cbind(xseq,CI95,PI95[,-1]))
                    colnames(df) <- c("x1", "fit","IC_L","IC_U", "IP_L","IP_U")
                    df
                    }

```


## Examples

Do not execute, it's just a syntax example.
<!-- Falta describir el ejemplo y que corra.... -->

```{r, warning=FALSE, message=FALSE, eval = FALSE}
IC <- fn_intervals(eq,xseq)
```
