---
title: "fn_R2RV  {Morefi}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_R2RV  {Morefi}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Robust version of the coefficient of determination

## Description

The function calculates a robust version of the coefficient of determination $R^{2}_{RV}$

This is the consistency corrected robust coefficient of determination by Renaud and Victoria-Feser (2010) which allows for a possible correction factor **a** for consistency considerations.

Inside the function:

  The vectors of observed (**y1**), predicted (**yc**) and weighted (**W**) values are obtained from the summary model (**eq**).

  The value of the Weighted Estimate Average (**ywea**), the  modified sum of squares for explained (**SSEw**), total (**SSTw**), and residual (**SSRw**) were estimated.

  A vector with the robust version of the coefficient of determination **R2wa** and its adjusted value **R2wa_adj** were returned as a vector.


In the function, the following were estimated:

The Weighted Estimate Average $\overline{\widehat{y}}_{w}$  (called as **ywea**).
  
$$\overline{\widehat{y}}_{w}=\left(1/\Sigma w_{i}\right)\times \Sigma w_{i} \widehat{y}_{i}$$


The modified sum of squares explained **SSEw**
$$SSEw= \sum_{}^{}w_{i}(\widehat{y}_{i}-\overline{\widehat{y}}_{w}) ^2)$$
The modified sum of squared residuals **SSRw**
$$SSRw= \sum_{}^{}w_{i}(y1_{i}-\widehat{y}_{i}) ^2)$$

The robust version of the coefficient of determination $R^{2}_{w,a}$ 
$$R^{2}_{w,a}=\frac{SSEw}{SSEw+a\times SSRw}$$
The adjusted coefficient of determination $R^{2}_{adj,w,a}$
$$R^{2}_{adj,w,a}=1- \left(1- R^{2}_{w,a}\right)\times \left( \frac{n-1 }{n-q} \right)$$


where $y1_{i}$, and $\widehat{y}_{i}$ are the $i_{th}$ observed and predicted 
values, $a$ is the correction factor value for consistency considerations 
(By default $a$ = 1), $n$ the number of pairs of observations and $q$ the number 
of variables included in the model.


The function requires defining:

 * **eq**: Summary of the equation fitted.
 * **a**:  the correction factor value for consistency considerations.

The function returns the a vector with the robust version of the coefficient of 
determination $R^{2}_{w,a}$ and its adjusted value $R^{2}_{adj,w,a}$.


## fn_R2RV


The function is included in the `Morefi` package **Morphological Relationships Fitted by Robust Regression**.


```{r setup}
library(Morefi)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
fn_R2RV <- function(eq,a=1){
      w <- eq$rweights   # w a vector of weights values
      yc <- eq$fitted.values # yc a vector of predicted values
      ywea <-  (1/sum(w)) * sum(w*yc) # a value of the Weighted Estimate Average
      y1 <- eq$model[,1]
      SSEw <- sum(w*(yc-ywea)^2)
      SSRw <- sum(w*(y1-yc)^2)
      a <- a
      R2wa <- SSEw/(SSEw+a*SSRw)
      R2wa_adj <- 1-(1-R2wa)*((length(y1)-1)/summary(eq)$df[2])
      R2was <- c(R2wa,R2wa_adj)
      print(R2was)
    }
```


## Examples


Do not execute, it's just a syntax example.
<!-- Falta describir el ejemplo y que corra.... -->

```{r, warning=FALSE, message=FALSE, eval = FALSE}
R2RV <- fn_R2RV(eq,a)
```


## References

Renaud, O., & Victoria-Feser, M. P. (2010). A robust coefficient of determination
for regression. Journal of Statistical Planning and Inference, 140(7), 1852-1862.
doi:10.1016/j.jspi.2010.01.008.
