---
title: "fn_summary {Morefi}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_summary {Morefi}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Customizes the summary of fitted regression

## Description

Table T1 is a customized table to store the regression summarized by
model and landed weight categories: Fresh, Frozen-thawed (Frozen) and
Total. The 95% confidence interval parameter is in parentheses.
The adjusted robust version of the coefficient of determination. (R2) and Degrees of Freedom (DF) are also reported.


List_Tables contains an empty T1 for each element (model) 

The function requires defining:


 * **List_Tables**: A list to store summary regression results.
 * **modelos**: A character vector containing the variables of a function.
 * **catego**: A character vector containing the landed weight categories.
 * **eq**: Summary of the equation fitted.
 * **R2**: A numeric value of the adjusted robust version of the coefficient of determination.
 * **i**: An integer value indicating the ith regression analyzed. 
 * **j**: An integer value indicating the jth categorie analyzed.


List_Tables with a customized table that stores the regression
summary of each model. 

seealso: lmrob() and nlrob() from robustbase (version 0.99-0)


## fn_summary


The function is included in the `Morefi` package (Morphological fit).


```{r setup}
library(Morefi)
```


The function is detailed below.


```{r, warning=FALSE, message=FALSE}
fn_summary <- function(List_Tables, modelos, catego, eq, R2, i, j){

  T1 <- List_Tables[[i]]
  lvar <- names(List_Tables[i])

  T1[1,1] <- ifelse (i<7,"Linear","Potential")
  T1[1,2] <- paste0(substr(lvar,1,2)," vs. ",
                    substr(lvar,3,nchar(lvar)))
  T1[j,3] <- catego[j]
  T1[j,4] <- eq$coefficients[1]                          # b0
  T1[j,5] <- paste0("(",round(confint.default(eq)[1,1],2)," to ",
                    round(confint.default(eq)[1,2],2), ")") #b0 IC95%
  T1[j,6] <- eq$coefficients[2]
  T1[j,7] <- paste0("(",round(confint.default(eq)[2,1],2)," to ",
                    round(confint.default(eq)[2,2],2), ")")
  T1[j,8] <- as.numeric(R2)
  T1[j,9] <- summary(eq)$df[2]

  print(T1[j,])

} # End fn_summary
```


## Examples


Do not execute, it's just a syntax example.
<!-- Falta describir el ejemplo y que corra.... -->

```{r, warning=FALSE, message=FALSE, eval = FALSE}
T1 <- fn_summary(List_Tables, modelos, catego, eq, R2, i, j)
```

