---
title: "fn_xseq  {Morefi}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_xseq  {Morefi}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Customizes the summary of fitted regression

## Description


The function generates a data frame with a sequence for independent variable
(including minimum and maximum values) and selects it according to the model.

The data frame should have the same column name as the dependent variable
used in the fitted model.

Inside the function, the appropriate sequence is selected in function of model
the mean **Ymean**, lower **Ymin**, and upper **Ymax** CI95% are stored in a table **Table_Y**


The function requires defining:

 * **modelos**: A list that defines the variables that will be taken into account for the model.
 * **List_x_seq**: A list to store the sequence of the independent variable considered for the ith fitted model.
 * **i**:  An integer value indicating the regression to be analyzed.
 

The function returns a one-column data frame with the sequence selected. 

seealso: seq() from base (version 4.3.0)


## fn_xseq


The function is included in the `Morefi` package **Morphological Relationships Fitted by Robust Regression**.


```{r setup}
library(Morefi)
```


The function is detailed below.


```{r, warning=FALSE, message=FALSE}
fn_xseq <- function(modelos,List_x_seq, i) {
  if (modelos[[i]][1]== 1) {
    xseq <- List_x_seq[[1]]
  } else {
      if (modelos[[i]][1]== 2) {
             xseq <- List_x_seq[[2]]
      } else {
            if (modelos[[i]][1]== 4) {
                  xseq <- List_x_seq[[3]]
            } else {
                  xseq <- List_x_seq[[4]]
      }  # End if                  
    }  # End if
  }  # End if
  xseq <- data.frame(x1=xseq)
} # End fn
```





## Examples


Do not execute, it's just a syntax example.
<!-- Falta describir el ejemplo y que corra.... -->

```{r, warning=FALSE, message=FALSE, eval = FALSE}
xseq <- fn_xseq(modelos,List_x_seq, i)
```
